### 2020-05-27 8_case_study.tex
Update case study wording.

In all cases, we found bugs that are applicable outside of Task Bench
and that impact metrics other than METG. Notably, the scalability
issues and asymptotic complexity have a growing impact with larger
node counts and will eventually become visible with nearly any
application. In other cases, we found performance degradation at the
extremes of application configurations which may be more difficult to
test with full-size applications, but which are nonetheless relevant
in strong-scaling regimes, particularly as node counts grow.

>>>>

In all cases, we found bugs that are applicable outside of Task Bench
and that impact metrics other than METG. Notably, the scalability
issues and asymptotic complexity have a growing impact with larger
node counts and will eventually become visible with nearly any
application. In other cases, Task Bench and METG made it possible to
identify performance degradation at the extremes of application
configurations which might remain hidden with full-size applications,
particularly when evaluated with weak and strong scaling alone. The
improvements motivated by our findings are nonetheless relevant in
strong-scaling regimes in a variety of applications, particularly as
node and core counts grow.
